Delocalization of Eigenvectors in Random Matrices

### 2025-03-21 Draft.tex
g40

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[blue, wavy] (u) to (y);
\draw[blue, ->] (alpha) to (y);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\draw[blue, <-] (alpha) to[bend right=30] (beta);
\draw[blue, ->] (x) to[bend left=60] (beta);
\draw[red, ->] (x) to [bend right=20] (y);
\end{tikzpicture}
\begin{equation*}
\mathcal{G}_{30, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}} G_{x\beta}S_{uv} B_{v\alpha}  S_{\alpha\beta}G_{\beta\alpha}G_{uy} B_{uy}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
\end{center}
Here, we eliminate first the edges  $\beta\textcolor{red}{\rightarrow}\alpha$ and $\alpha\textcolor{blue}{\rightarrow} y$ using estimate $(2)$, giving us a $O(W^{\delta_\sto/10}W^{-1}\eta_s^{-1/2})$ term. Due to the edge from $x\textcolor{blue}{\rightarrow}\beta$, we are not going to be summing $\alpha\leadsto\beta$ over $S_{ab}$ entries because it serves as a multiplicative term to the blue edge $x\textcolor{blue}{\rightarrow}\beta$. For this reason, we will apply the individual $S_{ab}\lesssim W^{-1}$ bound, s.t now summing over $x\textcolor{blue}{\rightarrow}\beta$ with estimate $(1)$ gives us a combined bound $O(W^{\delta_\sto/20}W^{1/2}\eta_s^{-3/4})$. Finally, by summing over the remaining wavy edges, starting with $\alpha, v$ and then $u$, due to the $O(1)$ term (estimate $(5)$), we get an estimate of the form:$\mathcal{G}_{30, s}\lesssim W^{3\delta_\sto/20}W^{-1/2}\eta_s^{-5/4}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (y) at (2, 0) {y};
\node (b) at (3, 0) {b};

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\draw[blue, wavy] (u) to (beta);
\draw[blue, ->] (alpha) to (y);
\draw[red, ->] (x) to [bend right=20] (y);
\draw[blue, <-] (alpha) to [bend left=15] (beta);
\draw[blue, ->] (x) to[bend left=60] (beta);
\end{tikzpicture}
\begin{equation*}
\mathcal{G}_{4, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}} G_{x\beta}  S_{uv} B_{v\alpha}S_{\alpha\beta}G_{\beta\alpha}B_{u\beta}G_{\alpha y}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
\end{center}
Here, we bound first the inner edges $\alpha\textcolor{blue}{\rightarrow} y$ and $\beta\textcolor{red}{\rightarrow}\alpha$, we get by estimate $(2)$ a combined term $\lesssim W^{-1}\eta_{s}^{-1/2}$. Again, by the same logic as above, we have to account for the individual term $\alpha\leadsto\beta$ instead of summing over it, retaining a $\lesssim W^{-1}$ term. By applying estimate $(1)$ for the edge $x\textcolor{blue}{\rightarrow}\beta$ and summing over the remaining wavy lines, we get the same bound as above, namely: 
$\mathcal{G}_{40, s}\lesssim W^{1/2}\eta_s^{-5/4}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (y) at (2, 0) {y};
\node (b) at (3, 0) {b};

>>>>

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[blue, wavy] (u) to (y);
\draw[blue, ->] (alpha) to (y);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\draw[blue, <-] (alpha) to[bend right=30] (beta);
\draw[blue, ->] (x) to[bend left=60] (beta);
\draw[red, ->] (x) to [bend right=20] (y);
\end{tikzpicture}
\begin{equation*}
\mathcal{G}_{30, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}} G_{x\beta}S_{uv} B_{v\alpha}  S_{\alpha\beta}G_{\beta\alpha}G_{uy} B_{uy}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
\end{center}
Here, we eliminate first the edges  $\beta\textcolor{red}{\rightarrow}\alpha$ and $\alpha\textcolor{blue}{\rightarrow} y$ using estimate $(2)$, giving us a $O(W^{\delta_\sto/10}W^{-1}\eta_s^{-1/2})$ term. Due to the edge from $x\textcolor{blue}{\rightarrow}\beta$, we are not going to be summing $\alpha\leadsto\beta$ over $S_{ab}$ entries because it serves as a multiplicative term to the blue edge $x\textcolor{blue}{\rightarrow}\beta$. For this reason, we will apply the individual $S_{ab}\lesssim W^{-1}$ bound, s.t now summing over $x\textcolor{blue}{\rightarrow}\beta$ with estimate $(1)$ gives us a combined bound $O(W^{\delta_\sto/20}W^{1/2}\eta_s^{-3/4})$. Finally, by summing over the remaining wavy edges, starting with $\alpha, v$ and then $u$, due to the $O(1)$ term (estimate $(5)$), we get an estimate of the form: $\mathcal{G}_{30, s}\lesssim W^{3\delta_\sto/20}W^{-1/2}\eta_s^{-5/4}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (y) at (2, 0) {y};
\node (b) at (3, 0) {b};

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\draw[blue, wavy] (u) to (beta);
\draw[blue, ->] (alpha) to (y);
\draw[red, ->] (x) to [bend right=20] (y);
\draw[blue, <-] (alpha) to [bend left=15] (beta);
\draw[blue, ->] (x) to[bend left=60] (beta);
\end{tikzpicture}
\begin{equation*}
\mathcal{G}_{4, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}} G_{x\beta}  S_{uv} B_{v\alpha}S_{\alpha\beta}G_{\beta\alpha}B_{u\beta}G_{\alpha y}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
\end{center}
Here, we bound first the inner edges $\alpha\textcolor{blue}{\rightarrow} y$ and $\beta\textcolor{red}{\rightarrow}\alpha$, we get by estimate $(2)$ a combined term $\lesssim O(W^{\delta_\sto/10}W^{-1}\eta_{s}^{-1/2})$. Again, by the same logic as above, we have to account for the individual term $\alpha\leadsto\beta$ instead of summing over it, retaining a $O(W^{-1})$ term. By applying estimate $(1)$ for the edge $x\textcolor{blue}{\rightarrow}\beta$ and summing over the remaining wavy lines, we get the same bound as above, namely: 
$\mathcal{G}_{40, s}\lesssim  W^{3\delta_\sto/20}W^{-1/2}\eta_s^{-5/4}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (y) at (2, 0) {y};
\node (b) at (3, 0) {b};
